---
title: "Homework 6"
author: Zihan Yu
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(patchwork)
library(ggplot2)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  digits = 3
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

##Problem 2

Load and clean the data for regression analysis
```{r}
birthweight =
  read_csv(here::here("birthweight.csv")) %>%
  janitor::clean_names() %>%
  mutate(
    across(
      c("frace", "mrace"),
      ~ case_when(
        .x == 1 ~ "White",
        .x == 2 ~ "Black",
        .x == 3 ~ "Asian",
        .x == 4 ~ "Puero Rican",
        .x == 8 ~ "Other",
        .x == 9 ~ "Unknown"
      )
    ),
    across(where(is.character), as.factor),
    malform = case_when(malform == 0 ~ "absent",
                        malform == 1 ~ "present"),
    malform = as.factor(malform),
    babysex = case_when(babysex == 1 ~ "male",
                        babysex == 2 ~ "female") %>% as.factor()
  )
birthweight %>% skimr::skim_without_charts()
```

We fit a model in the following code. `bwt` is the outcome variable and `babysex`, `bhead`, `blength`, `delwt`, `gaweeks` and `wtgain` are predictors.  
```{r}
model_df <- birthweight %>%
  select(bwt, babysex, bhead, blength, delwt, gaweeks, wtgain)

mul_model = lm(bwt ~ ., data = model_df)
summary(mul_model)
```

```{r}
step(mul_model, direction = "backward")
```

Model 1 
```{r}
model1 <- lm(bwt ~ ., data = model_df)
summary(model1)

model1 %>% 
  broom::tidy() %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable()
```

```{r}
model_df <- model_df %>% 
  modelr::add_predictions(model1) %>% 
  modelr::add_residuals(model1)

model_df
```

In the graph, the dots are scattered around zero. There are a few outliers in the graph.
```{r}
model_df %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5) +
  labs(
    title = "Predictors vs. Residuals Plot",
    x = "Predictors",
    y = "Residuals"
  )
```

The density plot is relatively symmetric and residuals seem to be centered around zero.
```{r}
model_df %>% 
  ggplot(aes(x = resid)) +
  geom_density() +
  labs(
    title = "Residuals plot",
    x = "Residuals",
    y = "Density"
  )
```

Create other two models
```{r}
model2 <- lm(bwt ~ blength + gaweeks, data = birthweight)
summary(model2)

model2 %>% 
  broom::tidy() %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable()
```

```{r}
model3 <- lm(bwt ~ babysex * bhead * blength, data = birthweight)
summary(model3)

model3 %>% 
  broom::tidy() %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable()
```

Cross Validation
```{r}
cv =
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
cv_birthweight =
  cv %>% 
    mutate(
        model1 = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + wtgain, data = .x)),
        model2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
        model3 = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
    ) %>% 
    mutate(
        rmse1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
        rmse2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
        rmse3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y))
    )
```

Compare three models. Model1 has lowest RMSE, so it fits the data best. Model2 has obviously highest RMSE, so it is the worst out of three models.
```{r}
cv_birthweight %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin() +
  labs(
    title = "Compare Three Models",
    x = "Model",
    y = "rmse"
  )
```













